Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
review 2.4 Solving Optimization Problems with

In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as \textcolor{blue}{presented by}~\cite{Bjorner2014}. In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; $\nu$Z base function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as \textcolor{blue}{mentioned} in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.

@@

\begin{itemize}
\item{\textbf{maximize(T)}
\textcolor{blue}{this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}}
\item{\textbf{minimize(T)}
\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}}
\item{\textbf{Assert-Soft F : weight n}
the function \textit{assert-soft} adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
\end{itemize}

As an example, one can optimize $\left(K + W\right)$, which is subject to restrictions in $\left(K < 2\right)$ and $\left(W - K < 1\right)$. The expected result of this optimization problem described in the code below is $2$. In fact, the model generated by $\nu$Z shows that $K = 1$ and $W = 1$.

@@

\vspace{2 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as \textcolor{blue}{mentioned} in~\cite{Barth1995} and~\cite{Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

>>>>

In this study, the SMT solver Z3 is used to check for the satisfiability of formulas generated from the HW-SW partitioning problem, as \textcolor{blue}{presented by}~\cite{Bjorner2014}. In particular, we exploit the use of MaxSMT solver $\nu$Z, which is implemented on top of the SMT solver Z3, in order to solve optimization problems; the $\nu$Z main function is to optimize objective functions, which formulate optimized criteria, within the logical context of constraints.~$\nu$Z also includes an incremental version of the Maximum Resiliency (MaxRes), as \textcolor{blue}{mentioned} in~\cite{Federica2008}, in order to achieve Maximum Satisfiability (MaxSAT), as defined in~\cite{NarodytskaN} and a Simplex to solve numbers without defined patterns.

@@

\begin{itemize}
\item{\textbf{maximize(T)}
\textcolor{blue}{this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}}
\item{\textbf{minimize(T)}
\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized; the accepted types are the same as maximize function.}}
\item{\textbf{Assert-Soft F : weight n}
the function \textit{assert-soft} adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
\end{itemize}

As an example, one can optimize $\left(K + W\right)$, which is subject to restrictions in $\left(K < 2\right)$ and $\left(W - K < 1\right)$. The expected result of this optimization problem described in the code below is $2$. Indeed, the model generated by $\nu$Z shows that $K = 1$ and $W = 1$.

@@

\vspace{2 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO), as \textcolor{blue}{mentioned} in~\cite{Barth1995} and~\cite{Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode ``lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
